Who does big team science?

### 2022-05-13 03.data_analysis.Rmd
updates from last week
making pics

```{r}
library(dplyr)
library(bib2df)
library(rio)
library(tidyr)
library(ggplot2)
library(nlme)
library(RColorBrewer)
#### fix sau chins paper #### https://osf.io/gq92w/ 
```

@@

# will code job data ----
table(o_job$employment_summary_role_title)
o_job$our_job <- tolower(o_job$employment_summary_role_title)
o_job$our_job <- trimws(o_job$our_job)
o_job$our_job <- gsub("visit\\s*|visiting\\s*", "", o_job$our_job)
o_job$our_job <- gsub("ass\\. prof\\.|.*assistant professor.*", "assistant professor", o_job$our_job)
o_job$our_job <- gsub(".*associate professor.*", "associate professor", o_job$our_job)
o_job$our_job <- gsub(".*lecturer.*", "lecturer", o_job$our_job)
o_job$our_job <- gsub("assegnisti|.+post.+|juan de la cierva researcher|post-doc.*|postdoc.*", "post doc", o_job$our_job)
o_job$our_job <- gsub("borsisti|.*fellow.*", "fellow", o_job$our_job)
o_job$our_job <- gsub("academic|collaboratori|guest researcher|evaluation specialist|junior specialist|lab manager|personale esterno ed autonomi|research analyst|research associate|research scientist|researcher.*|scholar|senior statistician|special volunteer", "researcher", o_job$our_job)
o_job$our_job <- gsub(".*intern.*|research asistant", "research assistant", o_job$our_job)
o_job$our_job <- gsub("dottorandi|.*phd.*", "grad student", o_job$our_job)
o_job$our_job <- gsub(".*educator.*|teaching assistant", "lecturer", o_job$our_job)
o_job$our_job <- gsub(".*full.*professor.*", "full professor", o_job$our_job)
o_job$our_job <- gsub(".*head.*", "head", o_job$our_job)
o_job$our_job <- gsub("centennial professor|prof\\.|professor of cognitive analytics|proffessor.*|^temporal proffesor.*", "full professor", o_job$our_job)
table(o_job$our_job)

@@

o_ed_explode <- data.frame()
o_job_explode <- data.frame()

####ERIN YOU STILL HAVE TO DO THIS####
# for jobs fill in "current" or end date
# Find users with blanks
# For each one find the number of rows 
# If 1 then make 2022
# If more than 1 
# Use the lead or other end function 
o_job %>% filter(is.na(employment_summary_end_date_year_value)) %>% 
  select(ORCID, employment_summary_start_date_year_value, employment_summary_role_title)

@@

  temp <- o_ed %>% 
    filter(education_summary_end_date_year_value <= year) %>% 
    arrange(desc(education_summary_end_date_year_value)) %>% 
    filter(!duplicated(ORCID)) %>% 
    select(ORCID, education_summary_role_title, 
           education_summary_organization_address_country) %>% 
    mutate(year_merge = year)

@@

  temp2 <- o_job %>% 
    filter(employment_summary_end_date_year_value >= year) %>% 
    arrange(desc(employment_summary_end_date_year_value)) %>% 
    filter(!duplicated(ORCID)) %>% 
    select(ORCID, employment_summary_role_title, 
           employment_summary_organization_address_country) %>% 
    mutate(year_merge = year)

@@

```{r}
# hand code these into categories that make sense
table(o_job$employment_summary_role_title)
table(merged_df$employment_summary_role_title)

# table by year 
# graph by year 
```

@@

```{r}
# hand code these into categories that make sense
table(merged_df$education_summary_role_title)

# consider coding as 1, 2, 3, 4, etc. 
# table by year 
# graph by year 
```

### Author Bean Counting

@@

```{r}
# grab first X authors and last author
# and the last one for 10 - 49
num_grab <- 3

>>>>

```{r}
library(dplyr)
library(bib2df)
library(rio)
library(tidyr)
library(ggplot2)
library(nlme)
library(RColorBrewer)
current_year <- 2022
#### fix sau chins paper #### https://osf.io/gq92w/ 
```

@@

# will code job data ----
table(o_job$employment_summary_role_title)
o_job$our_job <- tolower(o_job$employment_summary_role_title)
o_job$our_job <- trimws(o_job$our_job)
o_job$our_job <- gsub("visit\\s*|visiting\\s*", "", o_job$our_job)
o_job$our_job <- gsub("ass\\. prof\\.|.*assistant professor.*", "assistant professor", o_job$our_job)
o_job$our_job <- gsub(".*associate professor.*", "associate professor", o_job$our_job)
o_job$our_job <- gsub(".*lecturer.*", "lecturer", o_job$our_job)
o_job$our_job <- gsub("assegnisti|.+post.+|juan de la cierva researcher|post-doc.*|postdoc.*", "post doc", o_job$our_job)
o_job$our_job <- gsub("borsisti|.*fellow.*", "fellow", o_job$our_job)
o_job$our_job <- gsub("academic|collaboratori|guest researcher|evaluation specialist|junior specialist|lab manager|personale esterno ed autonomi|research analyst|research associate|research scientist|researcher.*|scholar|senior statistician|special volunteer", "researcher", o_job$our_job)
o_job$our_job <- gsub(".*intern.*|research asistant", "research assistant", o_job$our_job)
o_job$our_job <- gsub("dottorandi|.*phd.*", "grad student", o_job$our_job)
o_job$our_job <- gsub(".*educator.*|teaching assistant", "lecturer", o_job$our_job)
o_job$our_job <- gsub(".*full.*professor.*", "professor", o_job$our_job)
o_job$our_job <- gsub(".*head.*", "head", o_job$our_job)
o_job$our_job <- gsub("centennial professor|prof\\.|professor of cognitive analytics|proffessor.*|^temporal proffesor.*", "professor", o_job$our_job)
table(o_job$our_job)

@@

# for jobs fill in "current" or end date
# Find users with blanks
employ_fix <- o_job %>% 
  filter(is.na(employment_summary_end_date_year_value)) %>% 
  select(ORCID, employment_summary_start_date_year_value, employment_summary_role_title) %>% 
  filter(!is.na(employment_summary_role_title)) %>% 
  pull(ORCID)

for (i in 1:length(employ_fix)){
  # For each one find the number of rows 
  temp_fix <- o_job %>% 
  #filter(is.na(employment_summary_end_date_year_value)) %>% 
  select(ORCID, employment_summary_start_date_year_value,
         employment_summary_end_date_year_value,
         employment_summary_role_title) %>% 
    filter(ORCID == employ_fix[i]) %>% 
    filter(!is.na(employment_summary_role_title))

  # if only one row, make it now
  if (nrow(temp_fix) == 1){
    o_job$employment_summary_end_date_year_value[
      o_job$ORCID == employ_fix[i] &
      !is.na(o_job$employment_summary_role_title)
      ] <- current_year
  }

  if (nrow(temp_fix) > 1){

    lead_values <- c(current_year,
                     o_job$employment_summary_start_date_year_value[
      o_job$ORCID == employ_fix[i] &
      !is.na(o_job$employment_summary_role_title)
    ])
    lead_values <- lead_values[-length(lead_values)]

    # Use the lead or other end function 
    for (q in 1:length(lead_values)){

      if (is.na(o_job$employment_summary_end_date_year_value[
        o_job$ORCID == employ_fix[i] &
        !is.na(o_job$employment_summary_role_title)
      ][q])) {

      o_job$employment_summary_end_date_year_value[
        o_job$ORCID == employ_fix[i] &
        !is.na(o_job$employment_summary_role_title)
      ][q] <- lead_values[q]

      } # close lead if only na

    } # close lead values loop

  } # close if more than one row

} # close for all users

# check when values don't make sense
o_job %>% 
  filter(employment_summary_end_date_year_value < employment_summary_start_date_year_value)

# make employment by year 
o_ed_explode <- data.frame()
o_job_explode <- data.frame()

@@

  temp <- o_ed %>% 
    filter(education_summary_end_date_year_value <= year) %>% 
    arrange(desc(education_summary_end_date_year_value)) %>% 
    filter(!duplicated(ORCID)) %>% 
    select(ORCID, education_summary_role_title, our_ed,
           education_summary_organization_address_country) %>% 
    mutate(year_merge = year)

@@

  temp2 <- o_job %>% 
    filter(employment_summary_end_date_year_value >= year) %>% 
    arrange(desc(employment_summary_end_date_year_value)) %>% 
    filter(!duplicated(ORCID)) %>% 
    select(ORCID, employment_summary_role_title, our_job,
           employment_summary_organization_address_country) %>% 
    mutate(year_merge = year)

@@

```{r}
merged_df$our_job <- factor(merged_df$our_job, 
                            levels = c("research assistant", 
                                       "post doc", 
                                       "researcher", 
                                       "lecturer", 
                                       "fellow",
                                       "assistant professor",
                                       "associate professor", 
                                       "professor", "head"),
                            labels = tools::toTitleCase(c("research assistant", 
                                       "post doc", 
                                       "researcher", 
                                       "lecturer", 
                                       "fellow",
                                       "assistant professor",
                                       "associate professor", 
                                       "professor", "head")))

employment_overall <- as.data.frame(table(merged_df$our_job)) %>% 
  arrange(desc(Freq)) %>% 
  mutate(Percent = Freq / sum(Freq) * 100)
employment_time <- as.data.frame(table(merged_df$our_job, merged_df$graph_year))

employment_time_plot <- ggplot(employment_time, aes(Var2, Freq, fill = Var1)) +
  geom_bar(position="stack", stat="identity") + 
  theme_classic() + 
  xlab("Publication Year") + 
  ylab("Number of Researchers") + 
  scale_fill_brewer(palette = "RdBu", name = "Employment Category")
```

@@

```{r}
merged_df$our_ed <- factor(merged_df$our_ed, 
                            levels = c("bachelor", 
                                       "masters", 
                                       "doctor"),
                            labels = tools::toTitleCase(c("bachelor", 
                                       "masters", 
                                       "doctor")))

education_overall <- as.data.frame(table(merged_df$our_ed)) %>% 
  arrange(desc(Freq)) %>% 
  mutate(Percent = Freq / sum(Freq) * 100)
education_time <- as.data.frame(table(merged_df$our_ed, merged_df$graph_year))

edu_colors <- brewer.pal(6, "RdBu")[c(1,3,6)]

education_time_plot <- ggplot(education_time, aes(Var2, Freq, fill = Var1)) +
  geom_bar(position="stack", stat="identity") + 
  theme_classic() + 
  xlab("Publication Year") + 
  ylab("Number of Researchers") + 
  scale_fill_manual(values = edu_colors, 
                    name = "Education Category")
```

### Types of Publications

@@

```{r}
# un regions grouping do this above 
# grab first X authors and last author
# and the last one for 10 - 49
num_grab <- 3

### 2022-05-13 04.manuscript.Rmd
making pics

**_Employment_**. 
- print out overall
- print out over time 
- comment on if all normal academic

**_Education_**. 
- print out overall
- print out over time

@@

>>>>

**_Employment_**. We will summarize the general employment categories of individuals at the time of publication, along with a summary for change over time.

**_Education_**. We will summarize the general education categories of individuals at the time of publication, along with a summary for change over time.

**_Types of Publications_**. We will summarize the coded types of publications for individuals and demonstrate the changes in types of publications over time visually. We will comment if more "open" type publications appear to be published, such as data-sets, preprints, and software.

@@

**_Employment_**. Overall, individuals **at the time of publication** in big team science publications are  `r employment_overall$Var1[1]` (`r format(employment_overall$Percent[1], nsmall = 1, digits = 1)`%) and `r employment_overall$Var1[2]` (`r format(employment_overall$Percent[2], nsmall = 1, digits = 1)`%), followed by smaller categories for `r employment_overall$Var1[3]` (`r format(employment_overall$Percent[3], nsmall = 1, digits = 1)`%), `r employment_overall$Var1[4]` (`r format(employment_overall$Percent[4], nsmall = 1, digits = 1)`%), `r employment_overall$Var1[5]` (`r format(employment_overall$Percent[5], nsmall = 1, digits = 1)`%), and `r employment_overall$Var1[6]` (`r format(employment_overall$Percent[6], nsmall = 1, digits = 1)`%). Here, we will talk about the figure below and how the trends occur across time. We will also comment on the number of jobs that would be considered "non-academic".

```{r figure3, echo = FALSE, warning = FALSE}
employment_time_plot
```

**_Education_**. Overall, individuals **at the time of publication** in big team science publications are  `r education_overall$Var1[1]` (`r format(education_overall$Percent[1], nsmall = 1, digits = 1)`%), `r education_overall$Var1[2]` (`r format(education_overall$Percent[2], nsmall = 1, digits = 1)`%), and`r education_overall$Var1[3]` (`r format(education_overall$Percent[3], nsmall = 1, digits = 1)`%). Here, we will talk about the figure below and how the trends occur across time.

```{r figure4, echo = FALSE, warning = FALSE}
education_time_plot
```

### 2022-05-13 04.manuscript.tex
making pics

@@

\begin{itemize}
\tightlist
\item
  The slope for year of first publication was \emph{b} = 0.00, \emph{SE} = 0.00, \emph{t}(53) = 1.71, \emph{p} = .092.
\item
  The variance parameter was \(SD\) = 7.99.
\item
  The slope for variance across years was \emph{b} = 0.01, \emph{SE} = 0.48, \emph{t}(23) = 0.02, \emph{p} = .983.
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  The slope for year of first publication was \emph{b} = 0.00, \emph{SE} = 0.00, \emph{t}(15) = 1.59, \emph{p} = .132.
\item
  The variance parameter was \(SD\) = 8.88.
\item
  The slope for variance across years was \emph{b} = 0.16, \emph{SE} = 0.61, \emph{t}(2) = 0.26, \emph{p} = .821.
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  The slope for year of first degree was \emph{b} = 0.00, \emph{SE} = 0.00, \emph{t}(35) = 5.14, \emph{p} = \textless{} .001.
\item
  The variance parameter was \(SD\) = 7.77.
\item
  The slope for variance across years was \emph{b} = 0.03, \emph{SE} = 0.82, \emph{t}(14) = 0.04, \emph{p} = .971.
\end{itemize}

@@

>>>>

\textbf{\emph{Employment}}. We will summarize the general employment categories of individuals at the time of publication, along with a summary for change over time.

\textbf{\emph{Education}}. We will summarize the general education categories of individuals at the time of publication, along with a summary for change over time.

\textbf{\emph{Types of Publications}}.
- print out overall
- print out over time
- open science question

\textbf{\emph{Publication Metrics}}.
- means and SDs for i10 and hindex information, and number of publications
- same analyses as career length - slope of number of publications and variance of number of publications
- slope up means people who are publishing more are more represented in the researchers
- slope down means more people with less publications
- answer are we giving opportunities to people who need the bean counting

\textbf{\emph{Geopolitical Regions}}.
- overall map of where people get their education
- overall map of where people are working
- is this diversifying over time (more countries as years go up)
- then the weird analysis to answer about diversifying authors

@@

\begin{itemize}
\tightlist
\item
  The slope for year of first publication was \emph{b} = 0.00, \emph{SE} = 0.00, \emph{t}(53) = 1.71, \emph{p} = .092.
\item
  The variance parameter was \emph{SD} = 7.99.
\item
  The slope for variance across years was \emph{b} = 0.01, \emph{SE} = 0.48, \emph{t}(23) = 0.02, \emph{p} = .983.
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  The slope for year of first publication was \emph{b} = 0.00, \emph{SE} = 0.00, \emph{t}(15) = 1.59, \emph{p} = .132.
\item
  The variance parameter was \emph{SD} = 8.88.
\item
  The slope for variance across years was \emph{b} = 0.16, \emph{SE} = 0.61, \emph{t}(2) = 0.26, \emph{p} = .821.
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  The slope for year of first degree was \emph{b} = 0.00, \emph{SE} = 0.00, \emph{t}(35) = 5.14, \emph{p} = \textless{} .001.
\item
  The variance parameter was \emph{SD} = 7.77.
\item
  The slope for variance across years was \emph{b} = 0.03, \emph{SE} = 0.82, \emph{t}(14) = 0.04, \emph{p} = .971.
\end{itemize}

@@

\textbf{\emph{Employment}}. Overall, individuals \textbf{at the time of publication} in big team science publications are Professor (28.8\%) and Assistant Professor (24.7\%), followed by smaller categories for Lecturer (16.4\%), Associate Professor ( 9.6\%), Post Doc (8.2\%), and Head (6.8\%). Here, we will talk about the figure below and how the trends occur across time. We will also comment on the number of jobs that would be considered ``non-academic.''

\includegraphics{04.manuscript_files/figure-latex/figure3-1.pdf}

\textbf{\emph{Education}}. Overall, individuals \textbf{at the time of publication} in big team science publications are Doctor (79.7\%), Masters (16.5\%), andBachelor (3.8\%). Here, we will talk about the figure below and how the trends occur across time.

\includegraphics{04.manuscript_files/figure-latex/figure4-1.pdf}

\textbf{\emph{Types of Publications}}.
- print out overall
- print out over time
- open science question

\textbf{\emph{Publication Metrics}}.
- means and SDs for i10 and hindex information, and number of publications
- same analyses as career length - slope of number of publications and variance of number of publications
- slope up means people who are publishing more are more represented in the researchers
- slope down means more people with less publications
- answer are we giving opportunities to people who need the bean counting

\textbf{\emph{Geopolitical Regions}}.
- overall map of where people get their education
- overall map of where people are working
- is this diversifying over time (more countries as years go up)
- then the weird analysis to answer about diversifying authors
